Dashboards for stock assessments: Getting started

### 2019-10-18 analysis/dashboards/getting_started.Rmd
Draft a crosstalk basics page to the getting_started dashboard

```{r setup, include=FALSE}
library(plotly)
library(crosstalk)
```

@@

This is where the output type is defined along with other items such as title, author, date, etc. A `flex_dashboard` is requested here. There are are growing number of output types supported by R markdown (e.g. html_document, pdf_document, word_document).

@@

```{r, echo = TRUE, eval = FALSE}
p <- ggplot(data = iris, 
            mapping = aes(x = Sepal.Length, 
                          y = Petal.Length, 
                          color = Species)) +
  geom_point() +
  scale_color_manual(values = viridis::viridis(3))
ggplotly(p)
```

@@

```{r}
p <- ggplot(data = iris, 
            mapping = aes(x = Sepal.Length, 
                          y = Petal.Length, 
                          color = Species)) +
  geom_point() +
  scale_color_manual(values = viridis::viridis(3))
ggplotly(p)
```

@@

```{r, echo = TRUE, eval = FALSE}
plot_ly(data = iris, 
        x = ~Sepal.Length, 
        y = ~Petal.Length, 
        color = ~Species,
        colors = viridis::viridis(3)) %>% 
  add_markers()
```

@@

The `plot_ly` function is analogus to the `ggplot` function from `ggplot2` and, like `ggplot`, this function sets-up the base layer of the plot. Again, the `iris` data is supplied and specific columns are mapped to `x`, `y` and `color` aesthetics.

@@

```{r}
plot_ly(data = iris, 
        x = ~Sepal.Length, 
        y = ~Petal.Length, 
        color = ~Species,
        colors = viridis::viridis(3)) %>% 
  add_markers()
```

@@

This skeleton is a verbatim copy of an R markdown file (extension `.Rmd`) set-up to produce a simple `flexdashboard` with interactive `plotly` visuals connected by `crosstalk`. Like most R markdown files, it includes three types of content:

@@

This is where the `plotly` and `crosstalk` packages are loaded along with some sample data. The sample data includes length and weight data (columns `length` and `weight`, respectively) along with fitted values and residuals from a length-weight regression (columns called `fit` and `res`, respectively). The `SharedData` function from `crosstalk` package is also used here to generate a data object that can be "shared" across independent plots.

>>>>

```{r setup, include=FALSE}
library(plotly)
library(leaflet)
library(crosstalk)
```

@@

This is where the output type is defined along with other items such as title, author, date, etc. A `flex_dashboard` is requested here. There are are growing number of output types supported by R markdown (e.g. `html_document`, `pdf_document`, `word_document`).

@@

```{r, echo = TRUE, eval = FALSE}
library(ggplot2)
p <- ggplot(data = iris, 
            mapping = aes(x = Sepal.Length, 
                          y = Petal.Length, 
                          color = Species)) +
  geom_point() +
  scale_color_manual(values = viridis::viridis(3))
plotly::ggplotly(p)
```

@@

```{r}
library(ggplot2)
p <- ggplot(data = iris, 
            mapping = aes(x = Sepal.Length, 
                          y = Petal.Length, 
                          color = Species)) +
  geom_point() +
  scale_color_manual(values = viridis::viridis(3))
plotly::ggplotly(p)
```

@@

```{r, echo = TRUE, eval = FALSE}
library(plotly)
plot_ly(data = iris, 
        x = ~Sepal.Length, 
        y = ~Petal.Length, 
        color = ~Species,
        colors = viridis::viridis(3)) %>% 
  add_markers()
```

@@

The `plot_ly` function is analogous to the `ggplot` function from `ggplot2` and, like `ggplot`, this function sets-up the base layer of the plot. Again, the `iris` data is supplied and specific columns are mapped to `x`, `y` and `color` aesthetics.

@@

```{r}
library(plotly)
plot_ly(data = iris, 
        x = ~Sepal.Length, 
        y = ~Petal.Length, 
        color = ~Species,
        colors = viridis::viridis(3)) %>% 
  add_markers()
```

crosstalk {data-navmenu="Basics" data-orientation=columns}
=======================================================================

The `crosstalk` package enables HTML widgets, such as `plotly` and `leaflet`, to communicate with each other without `shiny`. As such, self-contained html files with similar behaviour to `shiny` applications can be built using `crosstalk`.

A first step to using `crosstalk` is to set-up a shared data-set using the `SharedData` function:

```{r, echo = TRUE}
library(crosstalk)
sub_quakes <- subset(quakes, stations %in% c(10, 20, 50, 100))
shared_quakes <- SharedData$new(sub_quakes)
```

The `quakes` data is used for this example. As shown to the right using `leaflet` and `plotly`, HTML widgets using this shared data will be linked and selections in one plot will affect the other plot.

The `crosstalk` package also includes a series of functions for filtering the shared data (`filter_checkbox`, `filter_slider` and `filter_select`). When used in a `flexdashboard`, and other interactive contexts, the following lines of code will produce the check-box, slider and drop-down filters shown below.

```{r, echo = TRUE, eval = FALSE}
filter_checkbox("stations", "Stations", shared_quakes, 
                ~stations, inline = TRUE)
filter_slider("depth", "Depth", shared_quakes, ~depth)
filter_select("mag", "Magnitude", shared_quakes, 
              ~cut(mag, breaks = seq(1, 10, 0.5), right = FALSE))
```

```{r}
filter_checkbox("stations", "Stations", shared_quakes, 
                ~stations, inline = TRUE)
filter_slider("depth", "Depth", shared_quakes, ~depth)
filter_select("mag", "Magnitude", shared_quakes, 
              ~cut(mag, breaks = seq(1, 10, 0.5), right = FALSE))
```

Column
--------------------------------------

### leaflet

```{r}
leaflet(shared_quakes) %>%
  addTiles() %>%
  addCircleMarkers(stroke = FALSE,
                   fillOpacity = 0.5,
                   color = ~viridis::viridis(4)[factor(stations)])
```

```{r}
plot_ly(data = shared_quakes) %>% 
  add_markers(x = ~depth, 
              y = ~mag, 
              color = ~factor(stations),
              colors = viridis::viridis(4),
              marker = list(size = 15))
```

@@

This skeleton is a verbatim copy of an R markdown file (`` `r xfun::embed_file("skeleton.Rmd", text = "skeleton.Rmd")` ``) set-up to produce a simple `flexdashboard` with interactive `plotly` visuals connected by `crosstalk`. Like most R markdown files, it includes three types of content:

@@

This is where the `plotly` and `crosstalk` packages are loaded along with some sample data (`` `r xfun::embed_file("length-weight_data.csv", text = "length-weight_data.csv")` ``). The sample data includes length and weight data (columns `length` and `weight`, respectively) along with fitted values and residuals from a length-weight regression (columns called `fit` and `res`, respectively). The `SharedData` function from `crosstalk` package is also used here to generate a data object that can be "shared" across independent plots.
